Turnover of species and interactions

### 2018-10-26 paper/data-exploration/turnover.Rmd
Fix broken figures in exploration report

species_list %>%
  remove_unknown_species() %>% 
  get_sp_freq_by_group(sp_name) %>% 
  plot_freq_step() +
  labs(title = "number of locations per species", 
       subtitle = "turnover of species in the Web of Life database")

@@

interaction_list %>%
  remove_unknown_species() %>% 
  get_int_freq_by_group(pla_name, pol_name) %>% 
  plot_freq_step() +
  labs(litle = "locations per interactions", 
       subtitle = "turnover of interactions in the Web of Life database")
# 
# interaction_list %>% 
#   remove_unknown_species() %>% 
#   get_int_freq_by_group(pla_genus, pol_genus) %>% 
#   plot_freq_step() +
#   ggtitle("locations per interactions (genus)")
```

>>>>

species_list %>%
  remove_unknown_species() %>% 
  get_sp_freq_by_group(sp_name) %>% 
  plot_freq_step() +
  labs(title = "number of locations per species", 
       subtitle = "species turnover in the Web of Life database")

@@

interaction_list %>%
  remove_unknown_species() %>% 
  get_int_freq_by_group(pla_name, pol_name) %>% 
  plot_freq_step() +
  labs(title = "locations per interactions", 
       subtitle = "interactions turnover in the Web of Life database")
# 
# interaction_list %>% 
#   remove_unknown_species() %>% 
#   get_int_freq_by_group(pla_genus, pol_genus) %>% 
#   plot_freq_step() +
#   ggtitle("locations per interactions (genus)")
```
